Using Energy Smart Meter Data and Socio-Demographic Indicators to Understand Consumption in Relation to Deprivation Levels

### 2018-06-03 paper/Paper_1_v02.Rmd
image updates

```{r SM_PROP, echo=FALSE, fig.cap="Smart Meter Penetration in the UK", out.width = '100%'}
knitr::include_graphics('SM_PROP.jpg')
```

@@

```{r LISA, echo=FALSE, fig.cap="Local Morans I", out.width = '100%'}
knitr::include_graphics("Local_morans_I.jpg")
```

@@

```{r hourly, echo=FALSE, fig.cap="Hourly rates of Total Energy Consumption", out.width = '100%'}
knitr::include_graphics("Hourly.jpg")
```
There is also a clear AM peak between 07:30 and 08:00, confirming that energy usage increases as people begin their daily tasks, but dips off again as people go out to work. The lowest energy usage occurs between the hours of 01:00 and 04:30, but does not go as low as zero because of the ‘standby’ rate of energy usage, where only those appliances which are not switched off such as the fridge freezer or central heating are consuming energy (Wyatt 2013). The fact that energy usage does not dip this low at any other time of the day indicates that in some cases energy is consumed throughout the day because people are at home through illness, unemployement, caring duties or shift work.

@@

```{r daily, echo=FALSE, fig.cap="Daily rates of Total Energy Consumption", out.width = '100%'}
knitr::include_graphics("Daily.jpg")
```

```{r seasonal, echo=FALSE, fig.cap="Seasonal rates of Total Energy Consumption", out.width = '100%'}
knitr::include_graphics("Seasonal.jpg")
```

>>>>

```{r SM_PROP, echo=FALSE, fig.cap="Smart Meter Penetration in the UK", out.width = '100%'}
knitr::include_graphics('images/SM_PROP.jpg')
```

@@

```{r LISA, echo=FALSE, fig.cap="Local Morans I", out.width = '100%'}
knitr::include_graphics("images/Local_morans_I.jpg")
```

@@

```{r hourly, echo=FALSE, fig.cap="Hourly rates of Total Energy Consumption", out.width = '100%'}
knitr::include_graphics("images/Hourly.jpg")
```
There is also a clear AM peak between 07:30 and 08:00, confirming that energy usage increases as people begin their daily tasks, but dips off again as people go out to work. The lowest energy usage occurs between the hours of 01:00 and 04:30, but does not go as low as zero because of the ‘standby’ rate of energy usage, where only those appliances which are not switched off such as the fridge freezer or central heating are consuming energy (Wyatt 2013). The fact that energy usage does not dip this low at any other time of the day indicates that in some cases energy is consumed throughout the day because people are at home through illness, unemployement, caring duties or shift work.

@@

```{r daily, echo=FALSE, fig.cap="Daily rates of Total Energy Consumption", out.width = '100%'}
knitr::include_graphics("images/Daily.jpg")
```

```{r seasonal, echo=FALSE, fig.cap="Seasonal rates of Total Energy Consumption", out.width = '100%'}
knitr::include_graphics("images/Seasonal.jpg")
```
